---
title: "Final Project (Coffee Survey)"
author: "Pawanpreet Gill"
format: html
echo: false
---

The "Great American Coffee Taste Test" was held in October 2023 by "world champion barista" James Hoffmann and coffee company Cometeer, where viewers filled out a survey about 4 coffees they ordered from Cometeer for the tasting. 

```{r}
#| warning: false
#| message: false
library(here)
library(gtsummary)
library(tidyverse)
coffee_survey1 <- readRDS(here::here("/Users/pawanpreetgill/Desktop/R Bootcamp/final-project/coffee_survey1.rds"))
```

# Descriptive statistics table using `tbl_summary()`
```{r}
#| label: tbl-one
#| tbl-cap: "This table shows descriptive statistics"
table1 <- tbl_summary(
	coffee_survey1,
	by = cups_bin,
	include = c(strength, roast_level, caffeine),
	label = list(
		strength ~ "Preferred coffee strength",
		roast_level ~ "Preferred coffee roast level",
		caffeine ~ "Preffered caffeine amount"
	),
	missing_text = "Missing")
table1
```

# Regression table
```{r}
#| label: tbl-two
#| tbl-cap: "This is a table with regression results"
tbl_uvregression(
	coffee_survey1,
	y = cups_bin,
	include = c(strength, roast_level, caffeine),
	method = lm)
```
As shown in @tbl-two, regression results of coffee strength, roast, and caffeine are shown by amount of cups drank in a day.

# Figure-Barplot
```{r}
#| label: fig-barplot
#| fig-cap: "This is a barplot that shows preferred roasts."
barplot(table(coffee_survey1$roast_level),
				main = "Barplot of Roast Levels",
				xlab = "Roast Level",
				ylab = "Frequency",
				col = "lightblue")
png(here("plots", "fig-barplot.png"))
```
As shown in @fig-barplot, light roast was the most popular.

# Writing/creating new function using poisson model
```{r}
poisson_model <- glm(cups_bin ~ strength + roast_level + caffeine,
										 data = coffee_survey1,
										 family = poisson)
tbl_regression(
	poisson_model,
	exponentiate = TRUE,
	label = list(
		strength ~ "Strength",
		roast_level ~ "Roast Level",
		caffeine ~ "Caffeine Amount"
	)
)
```

There were `r nrow(coffee_survey1)` participants.
`r inline_text(table1, variable = "roast_level", column = "stat_1")`
